\subsubsection{Scenarios}

\paragraph{Scenario 2.1}
Milan's Local PD cannot afford to send every morning several traffic cops to
prevent people from parking on the crosswalks, there are more urgent works to
do! But at the same time this type of infraction cannot be backed off. To fix
this problem, the Local PD can use \emph{Safe Streets}. A Local PD operator can
see from his screen all the reports regarding that specific type of violation
and then take action against them.

\paragraph{Scenario 2.2}
The city of Pesaro has activated \emph{SafeStreets} in its area two years ago
and it has also installed a system to keep track of traffic-related accidents,
in order to take advantage of the \emph{SmartSuggestions} feature.
Recently a lot of car crashes have been registered in the intersection between
via Venezia and via Milano, mainly because the cars from via Venezia didn't give
the other ones right of way.
In the same period, \emph{SafeStreets} has received numerous reports of cars
parked at the corners of that intersections.
\emph{SmartSuggestions} is able to cross the data and infer that the parked cars
might have obstructed the view of the drivers coming from via Venezia, who
failed to see the other cars approaching. So it emits a suggestion to build
\emph{bollards} to physically block illegal parking at the corners of the
intersection.
An employee of the local police logs into SafeStreets on his office computer and
check if there are any suggestions and the system shows the newly created one.
After brief considerations, the Police orders to build the suggested bollards,
so another operator comes back to SafeStreets and marks the action as
\emph{carried out}.
After a few weeks no more accidents have occurred at the intersection, so
\emph{SmartSuggestions} marks the suggested action as useful, and it will likely
propose it again in similar situations.