\section{Software System Attributes}
Here we provide a brief description of the desired attributes that the software
to be should have.

\subsection{Reliability}
The system should be able to run continuously without any interruptions.
To achieve this it should follow some basic principles of fault tolerance;
the preferred approach is active replications, since it also provides
scalability.

\subsection{Availability}
The system must be perceived as stable and must be there when users need it.
However it is not a life-critical system, so a limited downtime (e.g.\ for
maintenance) can be accepted. To sum up, the system must be available 99\% of
the time.

\subsection{Security}
Since the system will deal with personal data, security both in data storage
and in communication are key aspects.

All the \emph{communication} between the clients and servers, and also between
different data centers, must provide confidentiality, authentication and
integrity; this can be achieved, for example, by using the Transport Layer
Security protocol (TLS).

The \emph{data} stored by the system must be protected against unauthorized
access and passwords must not be stored as plaintext; a suggestion is to use
hashes and salt.

\subsection{Maintainability}
Another key aspect of the system is maintainability. In particular the design
must provide the flexibility to add new features on top of the existing ones.
It must also be easy to adapt the system to operate in other countries,
that may have different formats for personal and vehicle identifiers.

\subsection{Portability}
The system must provide a high level of compatibility with different devices
and technologies both on the client and the server sides.

On the \emph{client side} this means that the mobile application can run on the
major mobile operating systems (iOS and Android), without particular
restrictions on the OS version or specific device models. For the web part, this
means that the website must work in all the major web browsers.

On the \emph{server side} this means that the whole system must be broken up
into loosely coupled components that interact between themselves and with the
clients. The components should also be easy to substitute or move to a different
location (e.g.\ hosting provider).
These practices also increase the maintainability and scalability of the system.