\subsubsection{Scenarios}

\paragraph{Scenario 1.1}
Davide is a Professor Assistant at his University and lives five minutes away
from his office. He is a very healthy person, everyday he goes to his office by
bike, and most of the days he finds a car parked on the bicycle lot, so he has
to leave his bike in an unsafe place, where it can be stolen. Davide is
sick of this situation and wants to to something about it. He knows that the
Municipality of Milan recently deployed a new service: \emph{Safe Streets}, that
can be used to report situations like this. He downloads the App, registers,
logs in and then takes a picture of the car illegally parked on the bike lot.
The morning after Davide goes to his office as always by bike and to his
surprise the bike lot was free, so the new \emph{Safe Streets} works for real!

\paragraph{Scenario 1.2}
Carmelo is a man who lives in a small town in Sicily, but he's currently
planning to move to Catania for work reasons. In his hometown Carmelo has to live
with a very annoying problem: his neighbor often parks his car in front of
Carmelo's garage. So when Carmelo needs to use the car he usually finds the
exit blocked.
While looking for a new apartment in Catania, Carmelo finds out that the
Police has activated a new service called \emph{SafeStreets} that enables him
to see statistics of the reported parking violations.
Since he plans to use the car almost everyday to go to work, he doesn't want to
have the same problem he had in his hometown. So he decides to subscribe to the
service and looks for statistics about the \emph{parking in front of driveway}
violations. In this way he can identify the areas of the city where he's most
unlikely to find his garage entrance blocked by another car and look for
apartments there.

\paragraph{Scenario 1.3}
It's 8:15 AM in Milan and the tram 9, packed with commuters, is moving
in its reserved lane when it suddenly comes to an halt. The driver turns to
the passengers and clearly states: "another guy has parked his car on the tram
tracks, so we can't go on".
The passengers become very angry, because they know that they'll be late at
work. But luckily \emph{Vincenzo Brambilla}, a true milanese who is always up to
date with the latest technologies, exclaims "\emph{ghe pensi mi}" (i'll handle
this);
Vincenzo takes out his smartphone, opens the SafeStreets app, takes a photo at
the parked car, selects the \emph{vehicle on tram tracks} violation type and
sends the report to the local Police.
Within minutes, a tow truck arrives and takes the car away from the tracks,
so the tram can continue on its route.
