\section{Implementation plan}
In this section it will be showed how the various components will be developed
and the timing constraints they will need. 

From Figure \ref{fig:component_diagram}, it can be clearly seen that the
components don't have specific dependencies, so the development process can be
done in parallel. This is especially true if we consider that all the components
use RESTful communication and they are completely stateless. This means that
once one component has been developed, it can be immediately unit tested, even
the methods that require communication with other components can be tested, this
can be done by creating some \emph{ad-hoc stubs}.

Specifically, the order which the various components are implemented is not
fixed, except for \emph{Router}, \emph{SuggestionsEngine} and
\emph{DBMS/FileServer}. The main reason behind these choices is that, for
example, the Router is responsible only of taking care of the incoming requests
and forward them to the correct component, so it's role isn't critical in the
integration of the components, plus it's developing process is quite trivial. As
for the storage systems (DBMS and File Server), it is a common practice to test
the components using volatile memory, so a working database is not needed from
the very beginning. Note that this does not mean that the model of our world
won't be designed before the implementing phase. Indeed in this document an ER
Diagram of the DB is provided. As for SuggestionsEngine, it's complexity compels
us to start it's implementation as soon as possible. It's a machine learning
based component so the sooner it is ready, the better it is, because it can
start it's training and be truly ready for deployment.

Finally despite the fact the order, as previously stated is not important, some
components should be implemented in pairs. It's the case of \emph{Violation
Collector} and \emph{ViolationManager}, \emph{MunicipalityAPIWrapper} and
\emph{AccidentCollector}, \emph{StatisticsEngine} and
\emph{StatisticsRepresentationManager}. This can ben necessary as these pairs of
components work closely and their integration should be as easy as possible.